---
title: "project"
author: "Marco"
date: "17 de mayo de 2015"
output: html_document
---
## Downloading data

The data were downloaded with the next commands

URL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

download.file(URL, destfile = "training.csv", method="curl")

URL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

download.file(URL, destfile = "test.csv", method="curl")

Processing the data, I deleted the first column because it contained a consecutive number unuseful for the algoritm.

```{r}
data <- read.csv("training.csv", na.strings=c("NA", "#DIV/0!", ""), stringsAsFactors = T)
data <- data[,-1]
##classes <- sapply(data, class)
```

The code is very slow, and I see that there are many columns with NA, I looked for the sums of NA with this code colSums(is.na(data)), and I found that there are many columns with more than 19000 NA's, so I deleted the columns with more than 19 NAs, so I have 67 variables less (only 59 and before I had 160)

```{r}
##data <- data[,colSums(is.na(data))<19000]
colswithNA <- colSums(is.na(data))<19000
data <- data[,colswithNA]
```

We are going to predict the classe.
First I selected my training and test data set

```{r}
require(caret)
##require(grid); require(doMC);registerDoMC(6)
train=sample(1:nrow(data),11776)
inTrain <- createDataPartition(y=data$classe, p=0.6, list=F)
training <- data[inTrain,]
testing <- data[-inTrain,]
##modFit <- train(classe ~ ., method="rf", data=training, prox=T)
##modFit
```

Caret pakage was very slowly, so I used the RandomForest package to process my model

```{r}
set.seed(100)
library(randomForest)
model2 <- randomForest(classe~., data=training)
model2
```

The OOB estimate of  error rate was 0.18%, maybe this OOB error rate underestimate the true error

## Accuracy with the testing set


```{r}
set.seed(100)
predicted <- predict(model2,testing)
table(testing$classe, predicted)
```

This model is very accurate, I got only 3 errors from 7846 tests. So I can perform the submissions

Getting the answers for the submissions (these data were processed previously)

```{r}
##predicted <- predict(model2,test)
##predicted
```


```{r}
##pml_write_files = function(x){
#  n = length(x)
#  for(i in 1:n){
#    filename = paste0("problem_id_",i,".txt")
#    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col##.names=FALSE)
 # }
#}
```

```{r}
#pml_write_files(predicted)
```

